### 2021-03-11 paper_1.tex
finish Salient Object Detection

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/selective and non-selective pathways.png}
    \centering
    \caption{The flowchart of the porposed system}
    \label{fid: flowchart}
\end{figure}

@@

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/CBSP.png}
    \centering
    \caption{CBSP reconstruction}
    \label{fid: CBSP}
\end{figure}
Within the non-selective path, the crucial operation is to calculate the 
approximate spatial weights of salience based on the distribution of the previously 
detected contours. In this path there is the problem of determining 
the local information of each object. The solution to the problem is based 
on an operation that fills the regions delimited by these contours. A very 
efficient method proposed in \cite{0747815500} result is used for the extraction of the contours.
An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
The diameter divides the circle into two parts where, on each of these, for 
each pixel belonging to the edge, the average response of the edge (AER) will 
be calculated. This calculation is useful in deciding which of the two halves 
will belong to the salient region. Each spatial weight of salience is denoted 
by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$

@@

\subsubsection{\emph{Fixation Prediction}}
The prediction of fixation indicates the likelihood with which a human is 
looking at a given position in the scene. There are several metrics that are 
used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
and ROC (AUC). In the following article the ROC method is mainly used, 
on three types of datasets, to compare the proposed system with o already 
existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/ROC.png}
    \centering
    \caption{ROC comparison}
    \label{fig: ROC}
\end{figure}

@@

\subsubsection{\emph{Salient Object Detection}}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
    \centering
    \caption{The flowchart of the porposed system}
    \label{fid: flowchart}
\end{figure}

@@

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/CBSP.png}
    \centering
    \caption{CBSP reconstruction}
    \label{fid: CBSP}
\end{figure}
Within the non-selective path, the crucial operation is to calculate the 
approximate spatial weights of salience based on the distribution of the previously 
detected contours. In this path there is the problem of determining 
the local information of each object. The solution to the problem is based 
on an operation that fills the regions delimited by these contours. A very 
efficient method proposed in \cite{0747815500} result is used for the extraction of the contours.
An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
The diameter divides the circle into two parts where, on each of these, for 
each pixel belonging to the edge, the average response of the edge (AER) will 
be calculated. This calculation is useful in deciding which of the two halves 
will belong to the salient region. Each spatial weight of salience is denoted 
by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$

@@

\subsubsection{\emph{Fixation Prediction}}
The prediction of fixation indicates the likelihood with which a human is 
looking at a given position in the scene. There are several metrics that are 
used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
and ROC (AUC). In the following article the ROC method is mainly used, 
on three types of datasets, to compare the proposed system with o already 
existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
    \centering
    \caption{ROC comparison}
    \label{fig: ROC}
\end{figure}

@@

\subsubsection{\emph{Salient Object Detection}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
    \centering
    \caption{Metrics comparison}
    \label{fig: metrics}
\end{figure}
To compare the performance of the salient object detection, metrics such 
as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
results showed that for the first two metrics (P-R), systems such as HS and 
RF are the best, while for the F-score the proposed method is able to consider 
a greater range of thresholds. As it can be seen, in these two metrics the 
proposed system (CGVS (t2)) considers the central bias unlike the others. 
If the central bias were not considered, the results decrease but are still 
satisfactory (CGVS ''). However, in the remaining two metrics, the proposed 
system is the best, except in the PASCALS dataset where the best is the RF 
method.
